03 Data Vizualization

### 2023-01-06 03_data_viz.Rmd
SF sensitivity estimates

```{r, echo = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)    # CRAN v1.3.1    
library(forcats)      # CRAN v0.5.1      
#library(isoreader)    # CRAN v1.3.0    
#library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7 
#library(isotopia)     # [github::isoverse/isotopia] v0.5.8     
library(readxl)       # CRAN v1.3.1       
library(ggsci)        # CRAN v2.9        
library(ggborderline) # [github::wurli/ggborderline] v0.1.0 
library(ggrepel)      # CRAN v0.9.1      
library(latex2exp)    # CRAN v0.5.0    
library(ggdist)       # CRAN v3.0.0       
library(ggsignif)     # CRAN v0.6.2     
library(ggridges)     # CRAN v0.5.3     
library(cowplot)      # CRAN v1.1.1      
library(scales)       # CRAN v1.1.1
library(ggforce)      # Accelerating 'ggplot2', CRAN v0.3.3
```

@@

```{r}
# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromeleon.R"))
source(file.path("libs", "error_prop.R"))
source(file.path("libs", "calculate_turnover.R"))
source(file.path("libs", "turnover_to_gen.R"))
source(file.path("libs", "rename_FAs.R"))                
`%nin%` = Negate(`%in%`) # "Not In" function
var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
```

@@

```{r workspace images}
# Turnover data
turnover <- readRDS("cache/turnover_rates.RDS")

# Summarized turnover
turnover_summarized <- readRDS("cache/turnover_summarized.RDS")

# Weighted turnover data
turnover_weighted <- readRDS("cache/turnover_weighted.RDS")

@@

lit_turnover_w_ours <- lit_turnover %>% 
  bind_rows(turnover_means) %>% 
  # Convert to generation time:
  mutate(gen_d = turnover_to_gen(u_d_mn))
```

@@

## Memory effect on gen_d

```{r mean_generation_time}
p_gen_time_mean <- turnover_weighted %>% 
  select(c(terrain, inc_time_d, gen_d_weighted, gen_d_mc_weighted)) %>% 
  pivot_longer(cols = c(gen_d_weighted, gen_d_mc_weighted),
               values_to = "gen_d",
               names_to = "type") %>% 
  filter(inc_time_d == 7) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
  # group_by(terrain, inc_time_d) %>% 
  # summarize(terrain = terrain,
  #           gen_d_weighted = gen_d_weighted) %>% 
  # unique() %>% 
  # Plot it
  ggplot(aes(x = terrain,
             y = gen_d,
             fill = type)) +
  geom_col(width = 0.5,
           position = "dodge") +
  scale_fill_tron() +
  labs(x = "Soil Type",
       y = "Weighted Mean Generation Time (d)") +
  theme_classic() +
  theme()
p_gen_time_mean

cowplot::save_plot(
  plot = p_gen_time_mean,
  filename = "fig_output/generation_time_mean_mc.pdf",
  base_height = 4,
  base_width = 7
)
```

## F1A: dF plot
Using memory-corrected values

```{r}
p_dF <- turnover_summarized %>% 
  filter(
    compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF_mc, calibrated_at2H_with_memory_correction_se) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted_mc), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF_mc, dF_weighted_mc),
    values_to = "dF", 
    names_to = "type"
  ) %>% 
  mutate(compound = case_when(
    type == "dF_weighted_mc" ~ "Weighted Mean",
    TRUE ~ compound
  )) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tunrda"
  )) %>%

  ggplot(
    aes(
      x = inc_time_d,
      y = dF * 10000, # convert from at% to ppm
      group = compound,
      color = terrain,
      fill = terrain,
      alpha = type,
      size = type
    )
  ) +
  geom_point() +
  geom_line() +
  facet_wrap(vars(terrain)) +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  scale_alpha_discrete(range = c(0.2, 1)) +
  scale_size_discrete(range = c(1.5, 2)) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  theme_classic() +
  labs(
    x = "Time elapsed (days)",
    y = TeX("$ \\Delta ^2H$ (ppm)")
  ) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10),
        panel.grid.major.y = element_line(linetype = "dotted"))
p_dF

cowplot::save_plot(
  filename = "fig_output/p_dF.pdf",
  plot = p_dF,
  base_width = 11,
  base_height = 4
  )

```{r}
p_dF2 <- turnover_summarized %>% 
  filter(
    compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF_mc, calibrated_at2H_with_memory_correction_se) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted_mc), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF_mc, dF_weighted_mc),
    values_to = "dF", 
    names_to = "type"
  ) %>% 
  mutate(compound = case_when(
    type == "dF_weighted_mc" ~ "Weighted Mean",
    TRUE ~ compound
  )) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tunrda"
  )) %>%

  ggplot(
    aes(
      x = inc_time_d,
      y = dF * 10000, # convert from at% to ppm
      group = compound,
      color = terrain,
      fill = terrain,
      alpha = type,
      size = type
    )
  ) +
  geom_borderline(
    color = "gray",
    alpha = 1,
    size = 0.5
    ) +
  geom_point() +
  facet_wrap(vars(terrain)) +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  scale_alpha_discrete(range = c(0.2, 1)) +
  scale_size_discrete(range = c(1.5, 2)) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  theme_classic() +
  labs(
    x = "Time elapsed (days)",
    y = TeX("$ \\Delta ^2H$ (ppm)")
  ) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10),
        panel.grid.major.y = element_line(linetype = "dotted"))
p_dF2

## F1B: Turnover plot

@@

  # Plot it
  ggplot(
    aes(
      x = u_d_mc,
      y = compound,
      color = type,
      fill = type,
      label = round(gen_d_mc, 2)
      )
  ) +
    geom_point(size = 3) +
    geom_errorbar(aes(
      xmin = u_d_mc - (0.5 * su_d_mc),
      xmax = u_d_mc + (0.5 * su_d_mc)),
      width = 0,
      size = 1.1
      ) +
    #Uncomment to show generation times
    geom_text(
      nudge_x = 0.05
    ) +
    coord_cartesian(xlim = c(0, 0.175)) +
    scale_fill_manual(values = c("black", color_choice)) +
    scale_color_manual(values = c("black", color_choice)) +
    theme_classic() +
    labs(x = TeX("Turnover ($day^{-1}$)"),
         title = terrain_choice) +
    theme(
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.ticks.y = element_blank(),
      strip.background = element_blank(),
      legend.position = "none",
      plot.title = element_text(hjust = 0.5),
      panel.grid.major.x = element_line(linetype = "dotted")
    )

@@

p_turnover
# 
# ggsave(
#   plot = p_turnover,
#   filename = "fig_output/turnover_plot.pdf",
#   device = cairo_pdf, # Need this for greek symbols to render correctly
#   width = 11,
#   height = 4
#   )

@@

turnover_fit_tidy <- broom::tidy(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
turnover_fit_glance <- broom::glance(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
writexl::write_xlsx(turnover_fit_tidy, path = "data_output/turnover_fit_lm.xlsx")
writexl::write_xlsx(turnover_fit_glance, path = "data_output/turnover_fit_lm_stats.xlsx")

p_abundance_v_turnover2 <- turnover %>% 
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(
    x = compound_ug_per_g_soil,
    y = u_d_mc
  )) +
  # Individual data points
  geom_point(
    aes(color = terrain),
    alpha = 0.6,
    ) +
  geom_polygon(
    data = hull_data,
    aes(
       fill = terrain,
       color = terrain
       ),
     show.legend = FALSE,
     alpha = 0.15,
     size = 0.15
    ) +
  geom_smooth(
    method = "lm",
    formula = "y~x",
    se = FALSE,
    color = "gray",
    size = 0.3,
    linetype = "dotted"
  ) +
  scale_color_manual(values = terrain_color_swatch) +
  theme_bw() +
  labs(
    x = "µg analyte (per g soil)",
    y = TeX("Compound-specific growth rate (day$^{-1}$)"),
    size = TeX("$ \\Delta ^2H$ (ppm)"),
    color = " "
  ) +
  theme(
    strip.background = element_blank(),
    legend.position = c(0.9, 0.55),
    legend.background = element_blank(),
    panel.grid = element_blank(),
  )
p_abundance_v_turnover2

cowplot::save_plot(filename = "fig_output/abundance_v_turnover_2p.pdf",
                   plot = p_abundance_v_turnover2,
                   base_height = 6,
                   base_width = 8)

@@

### Inset Plot

@@

```{r}
p_abundance_v_turnover_w_inset <- ggdraw(p_abundance_v_turnover2) +
  draw_plot(
    p_abundance_v_turnover_inset, 
    x = 0.63, 
    y = 0.63, 
    width = 0.35, 
    height = 0.35
    )
cowplot::save_plot(filename = "fig_output/abundance_v_turnover_w_inset.pdf",
                   plot = p_abundance_v_turnover_w_inset,
                   base_height = 6,
                   base_width = 8)
```

@@

# Colorblind friendly palette:
lit_values_swatch_3 <- c(
  "#20968d", # gray green
  "#6269EB", # blue
  "#E0187B", # pink
  "#26AFE1" # light blue 
  )
p_lit_turnover_w_ours2 <- lit_turnover_w_ours %>%
  filter(method_type != "Microscopy") %>% 
  ggplot(
  aes(
    x = -n,
    y = u_d_mn,
    fill = method_type,
    label = round(gen_d, 1)
    )
    ) +
  geom_col() +
  scale_fill_manual(
    values = lit_values_swatch_3
  ) +
  # scale_fill_viridis_d(
  #   begin = 0,
  #   end = 0.8
  # ) +
  coord_flip(ylim = c(0, 0.5)) +
  labs(
    y = TeX("Turnover (d$^{-1}$)"),
    fill = "Method"
  ) +
  theme_classic() +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.line.y = element_blank(),
    legend.position = c(0.85, 0.8),
    legend.background = element_rect(color = "black"),
    legend.text = element_text(size = 15),
    legend.title = element_blank(),
  )
p_lit_turnover_w_ours2
# 
# cowplot::save_plot(filename = "fig_output/literature_values_draft2.pdf",
#                    plot = p_lit_turnover_w_ours2,
#                    base_height = 8,
#                    base_width = 10)

@@

### Draft 2 Inset

```{r}
 p_lit_turnover_w_ours_inset <- lit_turnover_w_ours %>%
  filter(method_type != "Microscopy") %>%
  ggplot(
    aes(
      x = u_d_mn, 
      y = method_type,
      color = method_type
      )
  ) +
  geom_boxplot(width = 0.2) +
  coord_cartesian(xlim = c(0, 0.5)) +
  #ggdist::stat_pointinterval() +
  scale_color_manual(
    values = lit_values_swatch_3
  ) +
  labs(
    x = "",
    y = "",
    fill = "Method"
  ) +
  theme_classic() +
  theme(
    legend.position = "NA"
  )
p_lit_turnover_w_ours_inset
```

### Draw with inset

```{r}
p_literature2_w_inset <- ggdraw(p_lit_turnover_w_ours2) +
  draw_plot(
    p_lit_turnover_w_ours_inset, 
    x = 0.63, 
    y = 0.23, 
    width = 0.35, 
    height = 0.35
    )
p_literature2_w_inset
```

@@

## (DEPRECATED) Turnover plot

```{r turnover_plots}
add_weighted_mean <- function(df) {
  df %>% 
    ungroup() %>% 
    mutate(type = "sample") %>% 
    add_row(compound = "Weighted Mean",
            u_d_weighted = df$u_d_weighted[1],
            terrain = df$terrain[1],
            u_d = df$u_d_weighted[1],
            type = "Weighted Mean")
}

# Add weighted generation time

summarized_weighted_gen_d <- gen_calc_data_summarized_weighted %>% 
  filter(inc_time_d == 7) %>% 
  select(terrain, gen_d_weighted) %>% 
  unique()

p_conifer_u_d <- gen_calc_data_summarized_weighted %>%
  filter(terrain == "Gordon Gulch Conifer Forest",
         inc_time_d == 7) %>% 
  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>%
  add_weighted_mean() %>% 
  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
  # PLOT IT
  ggplot() +
  geom_col(aes(x = compound,
               y = u_d, 
               fill = type)) +
  scale_fill_manual(values = c("#000000", conifer_color)) +
  # Secondary axis option:
  # scale_y_continuous(sec.axis = sec_axis(trans = ~ log(2)/.,
  #                                        breaks = c(7, 14, 30, 90, 365),
  #                                        name = "Generation time (d)")) +
  coord_flip(ylim = c(0, 0.09), clip = "off") +
  labs(y = TeX("Turnover ($d^{-1}$)"),
       title = "Conifer Forest") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5))
p_conifer_u_d

p_grassland_u_d <- gen_calc_data_summarized_weighted %>% 
  filter(terrain == "Marshall Mesa Grassland",
         inc_time_d == 7) %>% 
  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>% 
  add_weighted_mean() %>% 
  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
  # PLOT IT
  ggplot() +
  geom_col(aes(x = compound, y = u_d, fill = type)) +
  scale_fill_manual(values = c("#000000", grassland_color)) +
  coord_flip(ylim = c(0, 0.09), clip = "off") +
  labs(y = TeX("Turnover ($d^{-1}$)"),
       title = "Grassland") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5))

p_tundra_u_d <- gen_calc_data_summarized_weighted %>% 
  filter(terrain == "Niwot Ridge Tundra",
         inc_time_d == 7) %>% 
  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>% 
  add_weighted_mean() %>% 
  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
  # PLOT IT
  ggplot() +
  geom_col(aes(x = compound, y = u_d, fill = type)) +
  scale_fill_manual(values = c("#000000", tundra_color)) +
  # Add weighted generation time label
  coord_flip(ylim = c(0, 0.09), clip = "off") +
  labs(y = TeX("Turnover ($d^{-1}$)"),
       title = "Tundra") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5))
p_tundra_u_d
```

```{r moo}
# HORIZONTAL
p_turnover_enrichment_cow_h <- cowplot::plot_grid(
  p_conifer_2H,
  p_grassland_2H,
  p_tundra_2H,
  p_conifer_u_d,
  p_grassland_u_d,
  p_tundra_u_d,
  labels = "AUTO",
  rel_widths = c(1,1),
  align = "h",
  nrow = 2
)

p_turnover_enrichment_cow_h
# 
# cowplot::save_plot(filename = "fig_output/p_turnover_enrichment_cow_horiz.pdf",
#           plot = p_turnover_enrichment_cow,
#           base_height = 8,
#           base_width = 12
#           )

>>>>

```{r, echo = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)    # CRAN v1.3.1    
library(forcats)      # CRAN v0.5.1      
#library(isoreader)    # CRAN v1.3.0    
#library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7 
#library(isotopia)     # [github::isoverse/isotopia] v0.5.8     
library(readxl)       # CRAN v1.3.1       
library(ggsci)        # CRAN v2.9        
library(ggborderline) # [github::wurli/ggborderline] v0.1.0 
library(ggrepel)      # CRAN v0.9.1      
library(latex2exp)    # CRAN v0.5.0    
library(ggdist)       # CRAN v3.0.0       
library(ggsignif)     # CRAN v0.6.2     
library(ggridges)     # CRAN v0.5.3     
library(cowplot)      # CRAN v1.1.1      
library(scales)       # CRAN v1.1.1
library(ggforce)      # Accelerating 'ggplot2', CRAN v0.3.3
library(Cairo)
```

@@

```{r}
# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromeleon.R"))
source(file.path("libs", "error_prop.R"))
source(file.path("libs", "calculate_turnover.R"))
source(file.path("libs", "turnover_to_gen.R"))
source(file.path("libs", "rename_FAs.R"))
source(file.path("libs", "d2H_to_2F.R"))
`%nin%` = Negate(`%in%`) # "Not In" function
var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
```

@@

```{r workspace images}
# Turnover rates
turnover <- readRDS("cache/turnover_rates.RDS")

# Turnover rates averaged across experimental replicates
turnover_summarized <- readRDS("cache/turnover_summarized.RDS")

# Turnover rates averaged across 3d, 7d, experimental replicates
turnover_summarized_avg <- readRDS("cache/turnover_summarized_avg.RDS")

# Abundance-weighted turnover rates
turnover_weighted <- readRDS("cache/turnover_weighted.RDS")

# Abundance-weighted turnover rates averaged between 3d and 7d incubation time points
turnover_weighted_avg <- readRDS("cache/turnover_weighted_avg")

@@

lit_turnover_w_ours <- lit_turnover %>% 
  bind_rows(turnover_means) %>% 
  # Convert to generation time:
  mutate(gen_d = turnover_to_gen(u_d_mn)) %>% 
  filter(method_type != "Microscopy")
```

@@

## F1: dF and growth rate Plot

### 1A: dF plot

Using memory-corrected values

```{r}
p_dF <- turnover_summarized %>% 
  filter(
    compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF_mc, calibrated_at2H_with_memory_correction_se) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted_mc), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF_mc, dF_weighted_mc),
    values_to = "dF", 
    names_to = "type"
  ) %>% 
  mutate(compound = case_when(
    type == "dF_weighted_mc" ~ "Weighted Mean",
    TRUE ~ compound
  )) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>%

  ggplot(
    aes(
      x = inc_time_d,
      y = dF * 10000, # convert from at% to ppm
      group = compound,
      color = terrain,
      fill = terrain,
      alpha = type,
      size = type
    )
  ) +
  geom_point(alpha = 1) +
  geom_line() +
  facet_wrap(vars(terrain), scales = "free_y") +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  scale_alpha_discrete(range = c(1, 1)) +
  scale_size_discrete(range = c(0.25, 2)) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(ylim = c(0, 2500)) +
  theme_classic() +
  labs(
    x = "Time elapsed (days)",
    y = TeX("$ \\Delta ^2H$ (ppm)")
  ) +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(size = 14),
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_text(size = 10),
    panel.grid.major.y = element_line(linetype = "dotted"),
    panel.spacing = unit(1.75, "cm")
  )
p_dF

#plotly::ggplotly()
# 
# cowplot::save_plot(
#   filename = "fig_output/p_dF.pdf",
#   plot = p_dF,
#   base_width = 11,
#   base_height = 4
#   )
#   
```

### 1B: Growth rate plot

@@

  # Plot it
  ggplot(
    aes(
      x = u_d_mc,
      y = compound,
      color = type,
      fill = type,
      label = round(gen_d_mc, 2)
      )
  ) +
    geom_point(size = 3) +
    geom_errorbar(aes(
      xmin = u_d_mc - (0.5 * su_d_mc),
      xmax = u_d_mc + (0.5 * su_d_mc)),
      width = 0,
      size = 1.1
      ) +
    # #Uncomment to show generation times
    # geom_text(
    #   nudge_x = 0.05
    # ) +
    coord_cartesian(xlim = c(0, 0.25)) +
    scale_fill_manual(values = c("black", color_choice)) +
    scale_color_manual(values = c("black", color_choice)) +
    theme_classic() +
    labs(
      x = TeX("Compound-specific growth rate (day$^{-1}$)"),
      title = terrain_choice
      ) +
    theme(
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.ticks.y = element_blank(),
      strip.background = element_blank(),
      legend.position = "none",
      plot.title = element_text(hjust = 0.5),
      panel.grid.major.x = element_line(linetype = "dotted")
    )

@@

p_turnover

# ggsave(
#   plot = p_turnover,
#   filename = "fig_output/p_turnover.pdf",
#   device = cairo_pdf, # Need this for greek symbols to render correctly
#   width = 11,
#   height = 4
#   )

### Cowplot

```{r}
p_dF_ud <- cowplot::plot_grid(
  p_dF, p_turnover,
  nrow = 2,
  labels = "AUTO"
)
p_dF_ud

ggsave(filename = "fig_output/p_dF_ud.pdf", 
       plot = p_dF_ud,
       device = cairo_pdf, # required for rendering unicode symbols
       width = 11,
       height = 8)

@@

# Calculate summary statistics and export them
turnover_fit_tidy <- broom::tidy(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
turnover_fit_glance <- broom::glance(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))

turnover_corr_test <- broom::tidy(
  cor.test(
    x = turnover_cleaned$compound_ug_per_g_soil,
    y = turnover_cleaned$u_d_mc,
    method = "pearson"
  )
  )

writexl::write_xlsx(turnover_fit_tidy, path = "data_output/turnover_fit_lm.xlsx")
writexl::write_xlsx(turnover_fit_glance, path = "data_output/turnover_fit_lm_stats.xlsx")
writexl::write_xlsx(turnover_corr_test, path = "data_output/turnover_corr_test.xlsx")
```

# Plot it with the linear model!
p_abundance_v_turnover2 <- turnover %>% 
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(
    x = compound_ug_per_g_soil,
    y = u_d_mc
  )) +
  # stat_density_2d(
  #   geom = "polygon", 
  #   aes(
  #     alpha = after_stat(level),
  #     group = terrain,
  #     fill = terrain
  #     ),
  #   bins = 10
  #   ) +
  # Individual data points
  geom_point(
    aes(color = terrain),
    alpha = 0.6,
    ) +
  # Using Hull Data:
  geom_polygon(
    data = hull_data,
    aes(
       fill = terrain,
       color = terrain
       ),
     show.legend = FALSE,
     alpha = 0.15,
     size = 0.15
    ) +
  geom_smooth(
    method = "lm",
    formula = "y~x",
    se = FALSE,
    color = "gray",
    linewidth = 0.3,
    linetype = "dotted"
  ) +
  scale_color_manual(values = terrain_color_swatch) +
  #scale_fill_manual(values = terrain_color_swatch) +
  #scale_x_log10() +
  #scale_y_log10() +
  #scale_alpha_continuous(range = c(0,0.5)) +
  theme_bw() +
  labs(
    x = TeX("PLFA Concentration (µg $\\cdot g^{-1}$ soil)"),
    y = TeX("Compound-specific growth rate (day$^{-1}$)"),
    size = TeX("$ \\Delta ^2H$ (ppm)"),
    color = " "
  ) +
  theme(
    strip.background = element_blank(),
    legend.position = c(0.9, 0.55),
    legend.background = element_blank(),
    panel.grid = element_blank(),
  )
p_abundance_v_turnover2

# 
# cowplot::save_plot(filename = "fig_output/abundance_v_turnover_2p.pdf",
#                    plot = p_abundance_v_turnover2,
#                    base_height = 6,
#                    base_width = 8)

@@

### Inset: µ vs. 1/B

```{r}
total_biomass <- turnover_cleaned %>% 
  group_by(terrain) %>% 
  summarize(
    total_ug_per_g_soil = sum(compound_ug_per_g_soil, na.rm = TRUE)
  )

turnover_weighted_w_totals <- turnover_weighted %>% 
  filter(inc_time_d == 7) %>% 
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  left_join(total_biomass, by = "terrain")

b_ud_fit <- broom::tidy(
  lm(
    data = turnover_weighted_w_totals, 
    u_d_mc_weighted  ~ total_ug_per_g_soil
    )
  )
b_ud_stats <- broom::glance(
  lm(
    data = turnover_weighted_w_totals, 
    u_d_mc_weighted  ~ total_ug_per_g_soil
    )
)

p_turnover_totals <- turnover_weighted_w_totals %>% 
  ggplot(
    aes(
      x = total_ug_per_g_soil,
      y = u_d_mc_weighted
    )
  ) +
  geom_point(aes(color = terrain),
             size = 5) +
  # geom_smooth(
  #   method = "lm",
  #   formula = "y~x",
  #   se = FALSE,
  #   linetype = "dotted",
  #   color = "gray",
  #   size = 0.5
  # ) +
  scale_color_manual(values = terrain_color_swatch) +
  coord_cartesian(xlim = c(0, 3000), ylim = c(0.01, 0.05)) +
  labs(
    x = TeX("B (µg $\\cdot g^{-1}$ soil)"),
    y = TeX("Weighted mean \n growth rate (day$^{-1}$)"),
    color = ""
  ) +
  theme_bw() +
  theme(
    legend.position = "NA",
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10),
    axis.ticks.length = unit(-0.1, "cm"),
    panel.grid = element_blank()
  )
p_turnover_totals
```

```{r}
saveRDS(turnover_weighted_w_totals, file = "cache/turnover_weighted_w_totals.RDS")
```

```{r}
p_abundance_v_turnover_w_inset <- ggdraw(p_abundance_v_turnover2) +
  draw_plot(
    p_turnover_totals, 
    x = 0.65, 
    y = 0.63, 
    width = 0.33, 
    height = 0.35
    )
p_abundance_v_turnover_w_inset

cowplot::save_plot(filename = "fig_output/abundance_v_turnover_w_inset.pdf",
                   plot = p_abundance_v_turnover_w_inset,
                   base_height = 6,
                   base_width = 8)
```

### Inset: Zoom Plot (Deprecated)

@@

@@

# Colorblind friendly palette:
lit_values_swatch_3 <- c(
  "#6269EB", # blue
  "#20968d", # gray green
  "#26AFE1", # light blue 
  "#E0187B" # pink
  )

p_lit_turnover_w_ours2 <- lit_turnover_w_ours %>% 
  mutate(
    method_type = fct_relevel(method_type, c("LH-SIP", "DNA-SIP", "TdR/Leu", "Nutrient Budgeting"))) %>% 
  arrange(method_type, desc(u_d_mn)) %>% 
  mutate(
    m = seq(1,nrow(lit_turnover_w_ours))
  ) %>% 
  ggplot(
  aes(
    x = -m,
    y = u_d_mn,
    fill = method_type,
    label = round(gen_d, 1)
    )
    ) +
  geom_col() +
  geom_text(aes(
    label = format(round(gen_d, 1)),
    color = method_type
    ),
    nudge_y = .01
    )+
  scale_fill_manual(values = lit_values_swatch_3) +
  scale_color_manual(values = lit_values_swatch_3) +
  # scale_fill_viridis_d(
  #   begin = 0,
  #   end = 0.8
  # ) +
  coord_flip(ylim = c(0, 0.4)) +
  labs(
    y = TeX("Apparent Growth Rate (day$^{-1}$)"),
    fill = "Method"
  ) +
  theme_classic() +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.line.y = element_blank(),
    legend.position = c(0.85, 0.2),
    legend.background = element_rect(color = "black"),
    legend.text = element_text(size = 15),
    legend.title = element_blank(),
    panel.grid.major.x = element_line(linetype = "dotted")
  ) +
  guides(
    color = "none"
  )
p_lit_turnover_w_ours2

cowplot::save_plot(filename = "fig_output/literature_values_draft2.pdf",
                   plot = p_lit_turnover_w_ours2,
                   base_height = 8,
                   base_width = 10)

# Plot annotations
lit_turnover_w_ours %>% 
  group_by(method_type) %>% 
  summarize(
    gen_d_max = max(gen_d),
    gen_d_min = min(gen_d),
    gen_d_avg = mean(gen_d)
  )

@@

@@

## SF: Memory effect on gen_d and u_d

```{r mean_generation_time}
p_gen_time_mean <- turnover_weighted %>% 
  pivot_longer(
    cols = c(gen_d_weighted, gen_d_mc_weighted),
    names_to = "Correction",
    values_to = "gen_d"
  ) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
  # group_by(terrain, inc_time_d) %>% 
  # summarize(terrain = terrain,
  #           gen_d_weighted = gen_d_weighted) %>% 
  # unique() %>% 
  # Plot it
  ggplot(aes(x = terrain,
             y = gen_d,
             fill = Correction)) +
  geom_col(width = 0.5,
           position = "dodge") +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_manual(values = c("#4690b0", "#3d3d3d")) +
  labs(x = "Soil Type",
       y = "Weighted Mean Generation Time (d)") +
  theme_classic() +
  theme(
    legend.position = "NA",
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    )
p_gen_time_mean

p_ud_mean <- turnover_weighted %>% 
  pivot_longer(
    cols = c(u_d_weighted, u_d_mc_weighted),
    names_to = "Correction",
    values_to = "u_d"
  ) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>%
  # group_by(terrain, inc_time_d) %>% 
  # summarize(terrain = terrain,
  #           gen_d_weighted = gen_d_weighted) %>% 
  # unique() %>% 
  # Plot it
  ggplot(aes(x = terrain,
             y = u_d,
             fill = Correction)) +
  geom_col(width = 0.5,
           position = "dodge") +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_manual(values = c("#4690b0", "#3d3d3d")) +
  labs(
    x = "Soil Type",
    y = TeX("Weighted Mean Growth Rate $(d^{-1})$")
    ) +
  theme_classic() +
  theme(
    legend.position = "NA",
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    )
p_ud_mean

p_memcorr_effect <- cowplot::plot_grid(
  p_gen_time_mean,
  p_ud_mean,
  nrow = 1
)
p_memcorr_effect

cowplot::save_plot(
  plot = p_memcorr_effect,
  filename = "fig_output/memory_correction.pdf",
  base_height = 2.5,
  base_width = 6
)
```
